\thispagestyle{empty}

\chapter{Acknowledgements}


Firstly, I would like to express my gratitude to my thesis advisors, Reine Talj and Lounis Adouane, for their patience, assistance, and the relevance of their guidance. A PhD thesis is a somewhat adventurous experience, with an uncertain outcome; and it is partially thanks to them that I have completed mine.

I am also thankful to Philippe Martinet and Michel Basset for the honor of reviewing this dissertation, as well as to Véronique Cherfaoui and Olivier Simonin, who graciously agreed to contribute their efforts. I must not forget Maan El Badaoui El Najjar, who chaired the committee for my defense. I thank them all for their remarks and constructive criticisms.

Of course, I am grateful to all the fellow colleagues I have encountered during this thesis, in alphabetical order: Emmanuel Alao, Joelle Al Hage, Stéphane Bonnet, Maxime Escourrou, Chan He, Remy Huet, Antoine Lima, and Lahcene Mezouari.

The work presented in this dissertation is the result of three years of effort within the Heudiasyc laboratory, in the Computer Science Department of UTC. I wish to express my gratitude to all the members who contribute to making the work more enjoyable: my laboratory mates, the secretaries, and members of the logistics team, whose assistance I have appreciated.

Lastly, I extend my appreciation to the people who share my 6 pm to 11 pm, the fellow climbers from l'Association des Grimpeurs Compiégnois, Pauline, Emeline, Gérome, and all the other climbers. I am profoundly grateful to share my adventures with Maxime Noizet, Kiryan Devigne, and all my friends; their continuous support during these experiences was a game-changer. I thank my sister and brother for their unconditional care and kindness. To my beloved partner in crime, the being of light that inspires me to always push myself further. And to my beloved mother, my ocean of kindness.
 \clearpage