\appendix 
\thispagestyle{empty}

\hypertarget{AppendixB}{}\section*{Appendix B: Safety insurance strategy part of the inter-target distance matrix} 
The inter-target error $e_{f_{23}}$ is defined as given in \cite{8430659}: 

\begin{align} \label{eq:systeme_of_example}
    e_{f_{23}}&= f_2-f_3 \nonumber \\
    &=-f_2^{end} + f_2 + f_3^{end} - f_3 + f_2^{end} - f_3^{end} \nonumber \\
    &=-e_{f_2} + e_{f_3} + e_{f_{23}}^{end}
\end{align}

The inter-target distance can be expressed by: 
\begin{equation}\label{eq:derivative_inter_target}
    d_T^2 = e_{f_{23}}^Te_{f_{23}}
\end{equation}

eq. \ref{eq:derivative_inter_target} is derivated in order to obtain the minimum inter-target distance: 
\begin{align} \label{eq:distance_derivative}
    \frac{d(d_T^2)}{dt}&= 0 
\end{align}

eq. \ref{eq:derivative_inter_target} is replaced in eq. \ref{eq:distance_derivative}:
\begin{equation} \label{eq:nul_distane_derivative}
    2e_{f_{23}}^T\dot{e}_{f_{23}}=0
\end{equation}

eq. \ref{eq:nul_distane_derivative} can be written using the derivative of eq. \ref{eq:systeme_of_example} and eq. \ref{eq:linearSystem} as follows: 

\begin{align} \label{eq:system_A_remplacement}
    e_{f_{23}}^T\dot{e}_{f_{23}}&=0 \nonumber \\
    e_{f_{23}}^T[\dot{e}_{f_2} - \dot{e}_{f_3}]&=0 \nonumber \\
    e_{f_{23}}^T[(a_2+a_{23}){e}_{f_2} - (a_3 - a_{23}){e}_{f_3}]&=0
\end{align}

Using eq. \ref{eq:systeme_of_example} in eq. \ref{eq:system_A_remplacement}, it is obtained: 

\begin{align} \label{eq:final_condi_distance_CORM_2}
    e_{f_{23}}^T[(a_2+a_{23}){e}_{f_2} - (a_3 - a_{23})(e_{f_2} + {e}_{f_{23}} - {e}_{f_{23}}^{end})]&=0 \nonumber \\
  e_{f_{23}}^T[(a_2-a_3 +a_{23}){e}_{f_2} + (a_{23}-a_3){e}_{f_{23}} - (a_{23}-a_3){e}_{f_{23}}^{end}]&=0
\end{align}

Using  eq. \ref{eq:distance_derivative} and eq. \ref{eq:final_condi_distance_CORM_2}, the condition linking the minimum inter-target distance $\underline{D}_{T}$ and gains of the reconfiguration matrix $A$ can be formulated by: 

\begin{equation}\label{eq:FinalDistaneStudy}
    e_{f_{23}}^T \Big[\frac{a_2-a_3+a_{23}}{a_3-a_{23}}{e}_{f_2} + {e}_{f_{23}}^{end} \Big] \geq \underline{D}_{T} ^2 
\end{equation}

Thus, the values of $a_2$, $a_3$, and $a_{23}$ must be chosen to satisfy eq. \ref{eq:FinalDistaneStudy}.
